Gammapy: A Python package for gamma-ray astronomy

### 2023-01-26 src/ms-review.tex
Fix PDF build

%% \gammapy: concept and goals
%%% Question: starting date? Is is relevant, what is the real start?
The \gammapy project started based on the same idea as \astropuy with the objective of building a flexible and
efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
This is possible thanks to the definition of a standardised common data format such as the \gadf, and thanks to
an open development with a broad community of contributors. The relation of \gammapy to the
different instruments and the \gadf data format is illustrated in Figure~\ref{fig:big_picture}.

>>>>

%% \gammapy: concept and goals
%%% Question: starting date? Is is relevant, what is the real start?
The \gammapy project started based on the same idea as \astropy with the objective of building a flexible and
efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
This is possible thanks to the definition of a standardised common data format such as the \gadf, and thanks to
an open development with a broad community of contributors. The relation of \gammapy to the
different instruments and the \gadf data format is illustrated in Figure~\ref{fig:big_picture}.
